---
title: "App names suggested by Stage 2 students"
author: "Emma Rand"
date: "25/07/2019"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```

```{r pkgs}
library("kableExtra")
library("knitr")
library("flextable")
library("tidyverse")
library("wordcloud")
library("RColorBrewer")
```


# Survey 1
## Method
A call for participants to take part in a focus group was sent in the first week of the Autumn term 2018 to stage 2 students. This cohort of students had taken Data Analysis in R in the Spring term 2018, during their first year. Respondents were also able to suggest a name for the app, ask a question or make a comment.

```{r received-import}
categ <- read.table("data/suggested_names.txt",
                    sep = "/", 
                    header = TRUE,
                    stringsAsFactors = FALSE)
```


## Results
There were 39 respondents with an approximately 1:1:0 male: female:non-binary gender ratio which compares to ## 88:139:x for the cohort.  A total of 29 suggestions for App names were received and these were classified as expressing one or more of a set of X ideas concerned with outcomes for the user, the user experience, another app persona not related to either of those or left unclassified. See table 1

**Supplementary material**
```{r received-categ}
names(categ) <- c("Name suggested", "Categorisations")
categ %>% flextable() %>% 
  width(width = 2) %>% 
  fontsize(size = 9, part = "all",) %>% 
  add_header_lines("Table 1. Suggestions for the name of the App received through the call for focus-group participation") 

```





```{r}
# 
# names <- read.table("data/suggested_names.txt", sep = "\n", stringsAsFactors = FALSE)
# names(names) <- "responses"
# df <- data.frame(table(names))
# wordcloud(words = df$names,
#           freq = df$Freq, 
#           min.freq = 1,
#           random.order = FALSE,
#           rot.per = 0.35, 
#           colors = brewer.pal(4, "Dark2"))

```

